\section{Shrimp and grits}

\subsection*{Shrimp stock}

Peel \ing{1 pound medium fresh shrimp} set aside, reserving the shrimp shells.

In a large saucepan, bring \ing{6 cups water} to a boil over medium heat.
Add shrimp shells and reduce the heat to medium-low.
Cook for 15 to 20 minutes, stirring occasionally.
Cool the shrimp stock, and strain.
Discard the shells.

The {\it Grits} and {\it Shrimp} sections may be performed concurrently.

\subsection*{Grits}

In a large saucepan, bring 3.5 cups shrimp stock and 
\ing{1/2 teaspoon salt} to boil over medium heat.

Add \ing{3/4 cup white grits}.
Stir.

Add \ing{3 tablespoons butter}.
Stir until melted.

Cover, and reduce the heat to low.
Cook until thickened, stirring occasionally, about 15 to 20 minutes.

Add \ing{6 ounces pepper jack Velveeta cheese, cubed}, and stir until melted.
Set aside and keep warm.

\subsection*{Shrimp}

In a large skillet, heat \ing{3 tablespoons olive oil} over medium heat.

Add \ing{1.5 cups chopped Vidalia onion}.
Cook for 4 minutes.

Add \ing{1 red bell papper, chopped} and \ing{1 jalape\~{n}o, minced}.
Cook, stirring frequently, for 3 minutes.

Sprinkle with \ing{3 tablespoons flour}.
Stir constantly for 3 minutes.

Gradually add 2 cups of shrimp stock, stirring to scrape the bottom of the skillet and to prevent lumps. Bring the mixture to a boil, and cook until slightly thickened.

Add the shrimp, and cook until they turn pink, about 2 to 3 minutes.
Remove the skillet from the heat.

Add \ing{2 tablespoons heavy whipping cream}, \ing{1 teaspoon lime juice},
\ing{2 green onions, chopped}, \ing{3 tablespoons chopped cilantro}, 
\ing{1/2 teaspoon salt}, \ing{1/8 teaspoon ground black pepper}.
